Predicting Covid Data

### 2022-12-05 main.rmd
update intro and slides for mc results

## The MonteCarlo Study

- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error to predict future trends of covid data spread.
- Add more stuff here...

@@

@@

>>>>

## Introduction

- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
- They have then use the function to approximate the number of cumulative positive cases in Italy
- Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
- This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.

@@

## Overview of the Monte Carlo Simulation

- add more...

@@

# Monte Carlo Simulations

## China

## Italy

## Australia
